Parity-odd Neutrino Torque Detection

### 2018-10-24 neu_torque.tex
accuracy and nonlinear

\tcb{\textit{Discussion.---}} 
Accuracy and mass dependency: we notice that the cross-correlation coefficients between $\spin_0$ and initial values $\spin_L$ and $\spin_T$ are prominently higher than what was measured in \citep{2000ApJ...532L...5L}. We investigate that numerical errors that may affect the results. P3M (particle-particle particle-mesh) algorithms result in higher cross-correlation between initial and final spins, compared to PM (particle-mesh), where additional tangential forces in PM violate the angular momentum conservation. Higher mass halos in a given simulation generally have slightly higher $\mu_L$ and $\mu_I$, however the correlation is enhanced greatly as we use higher mass resolutions. All other cross-correlation measurements have only weak dependencies on the halo mass, even in a fixed simulation. With different box sizes, mass resolutions, force resolutions, and find that the results are consistent across these simulations. Especially, in the estimation of number of halo spins needed to detect the neutrino torque, the deciding number is the cross-correlation $\left\langle\spin^I_{\nu 0}\cdot\spin^{I_r}_\nu\right\rangle=0.19$. This has a very weak dependence on halo mass and configuration of the simulation.

Baryonic effects (+ etc.) in reconstruction and angular momentum conservation:

@@

Cosmic variance:

Bias:

cite later \citep{2018MNRAS.tmp.2447C}.

>>>>

\tcb{\textit{Discussion.---}} 
Accuracy and mass dependency: we notice that the cross-correlation coefficients between $\spin_0$ and initial values $\spin_L$ and $\spin_T$ are prominently higher than what was measured in \citep{2000ApJ...532L...5L}. We investigate that numerical errors that may affect the results. P3M (particle-particle particle-mesh) algorithms result in higher cross-correlation between initial and final spins, compared to PM (particle-mesh), where additional tangential forces in PM violate the angular momentum conservation. Higher mass halos in a given simulation generally have slightly higher $\mu_L$ and $\mu_I$, however the correlation is enhanced greatly as we use higher mass resolutions. All other cross-correlation measurements have only weak dependencies on the halo mass, even in a fixed simulation. With different box sizes, mass resolutions, force resolutions, and find that the results are consistent across these simulations. Especially, in the estimation of number of halo spins needed to detect the neutrino torque, the deciding number is the cross-correlation $\left\langle\spin^I_{\nu 0}\cdot\spin^{I_r}_\nu\right\rangle=0.19$. This has a very weak dependence on halo mass and configuration of the simulation. An accurate study of the neutrino torque requires mass and force resolutions to cover the wide range of halo mass, a large box size ($>600\,{\rm Mpc}/h$) to account the neutrino tides at distance, and neutrino particles or fluids to calculate more precise nonlinear neutrino effects. These require a simulation comparable to the computing resources of TianNu \citep{2017RAA....17...85E}.

@@

Codis \citep{2018MNRAS.tmp.2447C}.
